\input{title.tex}

### 2022-03-29 docs/papers/01_manuscript/01_introduction.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

% 制度的意义
Institutions (such as policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled system, including interplays between social actors, between ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
Understanding the complex interlinkages is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
Water governance tends to shift for institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
Some institutional shifts were reported to have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and in collaborative water governance systems in Europe \cite{green2013}).
However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not universal.
Therefore, despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, broader cascading effects of these changes are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.

>>>>

% 制度的意义
Institutions (such as policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled system, including interplays between social actors, between ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
Understanding the complex interlinkages is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
Water governance tends to shift for institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
Some institutional shifts were reported to have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and in collaborative water governance systems in Europe \cite{green2013}).
However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not ubiquitous.
Therefore, despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, broader cascading effects of these changes are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.

### 2022-03-29 docs/papers/01_manuscript/02_results.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

%! Author = songshgeo
%! Date = 2022/3/10
% \MakeUppercase{\subsection{Cascading effects of the institutional shifts}}
\subsection{Cascading effects of the institutional shifts}
\label{effects}
% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
% 从70年代黄河断流开始摸索87-WAS的初步治理方案，到98-UBR成功解决断流后于2008年强化该制度，黄河一直是中国水治理制度转变的先行者。
As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted completely since 2008.
% 1987年(87-WAS)和1998年(98-UBR)的制度变迁是YRB中两个被广泛认可的制度演变里程碑(图~\ref{fig:structure} \textit{S1 in  Supplementary  Methods})。
Throughout, the institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance (Figure~\ref{fig:structure} and \textit{S1 in Supplementary Material}).
Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{fig:structure}).

Here, we use Differenced Synthetic Control method, which considers economic growth and natural background, to estimate theoretical water uses scenarios without these policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
% 我们的结果表明，1987年(87-WAS)的制度转变实际上刺激了各省比没有干扰时使用更多的水，观测到比预期增加了10(图~\ref{fig:main_results}A和B)。
Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{fig:main_results}A).
% 在1998年制度再次改变后，用水量增加的趋势似乎被有效地抑制了，观察到的总用水量比预期减少了10(图~\ref{fig:main_results} C和D)。
However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed, with total observed water consumption decreasing by $260\%$ relative to the estimation (Figure~\ref{fig:main_results} B).
% 87-WAS后用水量的增加与1987 - 1998年地表径流严重干涸的事实相吻合，这是河流退化和环境危机的一个明显的试金石
The increased water uses after 87-WAS align with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
% 尽管在1998年制度转变后的十年内，干旱程度有增无减，但断流的环境危机却得到了有效解决。
On the other hand, although the density of droughts increased in the decade after the 98-UBR, the environmental crisis of river drying-up was effectively resolved (Figure~\ref{fig:main_results}C).
% 正如许多研究指出的，这主要是大规模制度变迁的成功
As literature has suggested, this institution shift contributed a lot to the successful water governance.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=32pc]{outputs/main_results2.jpg}
    \caption{
        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
        \textbf{A.} water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
        \textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR). While the blue lines are statistic water use data, grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
        \textbf{C.}
    }
    \label{fig:main_results}
\end{figure*}

% 然而，87-WAS 也非大多分析报告所认为的“没有起到效果”，因为制度变化完全没有产生影响时，流域的用水量将更接近我们的模型预测。
Furthermore, 87-WAS did not ``have no effect'' as previous analyses suggested because water uses will be closer to what our models predicted when the shift was a blank policy.
% 除了环境背景外，我们的预测还考虑了经济因素，假设经济总量与用水量之间的生产函数保持不变。
Besides environmental background, our forecast takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
% 由于单位水资源的生产效率在这一时期实际上保持了相似的趋势，这意味着流域用水量的加速增长不是经济增长的必然结果。
However, the production efficiency of unit water resources kept similar trends between provinces of the YRB and others (Figure \textit{S3 in Supplementary Material}), which means that the accelerated growth of basinal water uses was not the inevitable result of economic growth.
% 但实际上，我们的结果表明相对于正常的经济发展进程来说，黄河流域的水资源利用反而更像是受到了刺激。
However, our results suggest that water use (especially for irrigation) in the YRB was more likely to be partly stimulated by the shift in 1987 besides economic growth.
% 这种用水量的加速增长与制度设计时遏制用水、保护黄河流域有限的水资源的初衷相悖。
This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water.

% 两次制度转变带来的级联效应存在巨大差异
The cascading effects of the two institutional shifts were very different, while their reframed SES structures have direct differences.
% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
In our study period, the institution shifted between three different structures (XXX, XXX, and XXX) (Figure~\ref{fig:structure}).
%! 这里还是需要名字的
% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
% 这意味着，而与生态节点直接联系的各利益相关者之间没有横向连接。
Thus, until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological sections.
% 许多不同领域的经验研究指出这种结构很可能是错配的，因为这些利益相关者难以从全局出发维护好互相联系的生态系统。
Empirical studies in many different fields indicate that this structure is likely to be mismatched, as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
% 87-WAS带来的效果再一次说明了这种阻碍可持续性的治理结构需要得到重视。
The cascading effect of the 87-WAS once again demonstrates that the more stakeholders, the more difficult it is to have a win-win situation of environment and interests \cite{hegwood2021} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

>>>>

%! Author = songshgeo
%! Date = 2022/3/10
% \MakeUppercase{\subsection{Cascading effects of the institutional shifts}}
\subsection{Institutional shifts effect on water use}
\label{effects}
% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
% 从70年代黄河断流开始摸索87-WAS的初步治理方案，到98-UBR成功解决断流后于2008年强化该制度，黄河一直是中国水治理制度转变的先行者。
As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted entirely since 2008.
% 1987年(87-WAS)和1998年(98-UBR)的制度变迁是YRB中两个被广泛认可的制度演变里程碑(图~\ref{structure} \textit{S1 in  Supplementary  Methods})。
Throughout, the institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance (Figure~\ref{structure} and \textit{S1 in Supplementary Material}).
Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{structure}).

Here, we use Differenced Synthetic Control method, which considers economic growth and natural background, to estimate theoretical water uses scenarios without these policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
% 我们的结果表明，1987年(87-WAS)的制度转变实际上刺激了各省比没有干扰时使用更多的水，观测到比预期增加了10(图~\ref{main_results}A和B)。
Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{main_results}A).
% 在1998年制度再次改变后，用水量增加的趋势似乎被有效地抑制了，观察到的总用水量比预期减少了10(图~\ref{main_results} C和D)。
However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed, with total observed water consumption decreasing by $260\%$ relative to the estimation (Figure~\ref{main_results} B).
% 87-WAS后用水量的增加与1987 - 1998年地表径流严重干涸的事实相吻合，这是河流退化和环境危机的一个明显的试金石
The increased water uses after 87-WAS align with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
% 尽管在1998年制度转变后的十年内，干旱程度有增无减，但断流的环境危机却得到了有效解决。
On the other hand, although the density of droughts increased in the decade after the 98-UBR, the environmental crisis of river drying up was effectively resolved (Figure~\ref{main_results}C).
% 正如许多研究指出的，这主要是大规模制度变迁的成功
As literature has suggested, this institution shift contributed a lot to the successful water governance.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=32pc]{outputs/main_results2.jpg}
    \caption{
        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
        \textbf{A.} water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
        \textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR). While the blue lines are statistic water use data, the grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
        \textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. Size of the grey bubbles denotes the length of a drying up stream.
    }
    \label{main_results}
\end{figure*}

% 然而，87-WAS 也非大多分析报告所认为的“没有起到效果”，因为制度变化完全没有产生影响时，流域的用水量将更接近我们的模型预测。
Furthermore, 87-WAS did not ``have no effect'' as previous analyses suggested because water use will be closer to what our models predicted when the shift was a blank policy.
% 除了环境背景外，我们的预测还考虑了经济因素，假设经济总量与用水量之间的生产函数保持不变。
Besides environmental background, our forecast takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
% 由于单位水资源的生产效率在这一时期实际上保持了相似的趋势，这意味着流域用水量的加速增长不是经济增长的必然结果。
However, the production efficiency of unit water resources kept similar trends between provinces of the YRB and others (Figure \textit{S3 in Supplementary Material}), which means that the accelerated growth of basinal water uses was not the inevitable result of economic growth.
% 但实际上，我们的结果表明相对于正常的经济发展进程来说，黄河流域的水资源利用反而更像是受到了刺激。
However, our results suggest that water use (especially for irrigation) in the YRB was more likely to be partly stimulated by the shift in 1987 besides economic growth.
% 这种用水量的加速增长与制度设计时遏制用水、保护黄河流域有限的水资源的初衷相悖。
This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water.

% 两次制度转变带来的级联效应存在巨大差异
The cascading effects of the two institutional shifts were very different, while their reframed SES structures have direct differences.
% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
In our study period, the institution shifted between three different structures (Figure~\ref{structure} A to C).
% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
% 这意味着，而与生态节点直接联系的各利益相关者之间没有横向连接。
Thus, until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological sections.
% 许多不同领域的经验研究指出这种结构很可能是错配的，因为这些利益相关者难以从全局出发维护好互相联系的生态系统。
Empirical studies in many different fields indicate that this structure is likely to be mismatched, as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
% 87-WAS带来的效果再一次说明了这种阻碍可持续性的治理结构需要得到重视。
The cascading effect of the 87-WAS once again demonstrates that the more stakeholders, the more difficult it is to have a win-win situation of environment and interests \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

### 2022-03-29 docs/papers/01_manuscript/04_discussion.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

%! Author = songshgeo
%! Date = 2022/3/10
% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion. The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power. After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations. In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}. As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.

% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.

% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}. Following the institutional reforms of 1998, the Yellow River has not dried up since 1999. However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}. The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}). Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}. These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes. Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.

>>>>

%! Author = songshgeo
%! Date = 2022/3/10

\subsection{Novel insights and policy implications}
\label{insights}

% 由于87-WAS和98-UBR分别带来的两种结构在很多的SES中都是反复出现的构件，我们提出的机制对理解这类耦合系统至关重要
Since the structures introduced by 87-WAS and 98-UBR are recurring motifs in many SES, our proposed mechanism is crucial to understanding such coupled systems.
% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
Furthermore, we explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。
First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use. Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wang2019d,speed2013}; top-down regulations can trigger immediate institutional shifts, and sharp SES structural changes \cite{speed2013,roland2004}.
In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and clarifies the causal link between SES structure and outcome.
% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
Second, we can better understand the influence of structural alignments under a fixed basin by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB. Although socioeconomic units within a basin benefit from water resources in large river basins all over the world, and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1). Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in the SES institutional structure.
% 最后，我们的研究也存在一定局限性，那就是很难排除同期其他政策的效应。
Finally, one of the limitations of our method is that it is difficult to rule out the effects of other policies over the same time breakpoints.
% 然而，鉴于学者对于87-WAS与98-UBR两次制度转变的重要性基本达成共识，其结果差异仍对理解水治理有重要借鉴意义。
However, since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important references for understanding water governance.

% 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure formed by isolated stakeholders is not conducive to institutional solutions to environmental sustainability.
% 而随后 98-UBR 的成功从理论和实际上都佐证了制度尺度匹配的重要性，即需要强调与生态单元的尺度（这里是流域尺度）相符的代理人建立利益相关者之间的横向联系。
Moreover, the subsequent success of 98-UBR has proved the importance of institutional scale matching both theoretically and practically; that is, it is necessary to emphasize the establishment of potential connections between stakeholders by agents consistent with the scale of the ecological system (in this case, basinal scale and the YRCC).
Furthermore, according to our analysis of plausible scenario assumptions based on our model, when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future, the incentive distortion will be reinforced (see \textit{Supplementary Material S4}).
However, an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarth2002} of future water use would weaken incentive distortion (e.g., through water rights transfer) (see \textit{Supplementary Material S4}).
Policymakers can also propose a more dynamic institution by increasing the frequency of quota updates that responds to changing conditions will adapt more effectively to its social-ecological context (see \textit{Supplementary Material S4}).

% 未来的政策建议
% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yu2019}. Following the institutional reforms of 1998, the Yellow River has not dried up since 1999. However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wang2019a}. As a result, the Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}). Other SESs around the world face similar problems in establishing successful institutions for governance \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}. These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes. Our research provides a cautionary tale of how a mismatched structure of institutions can be a double-edged sword when attaining sustainability.
